On the minimum leaf conductance g~0~

### 2017-03-29 manuscript.Rmd
kala

---
title: "On the minimum leaf conductance g~0~"
author: ''
date: ''
output:
  html_document:
    theme: flatly
    number_sections: true
  word_document:
    reference_docx: manuscriptstyle.docx
csl: global-change-biology.csl
bibliography: references.bib
---

@@

We argue that

- we need g0 to get responses at low light correct, and probably at high T
- g0 is poorly estimated as the intercept, with the usual regression technique
- can we estimate g0 independently? Some assume that g0 = gdark (also @miner2017 !) but that's rubbish. It is also much larger than cuticular conductance, but seems roughly consistent with gmin (minimum conductance from leaf dry-down curves).
- there is inter-specific variation in gmin that is related to growth form 
- gmin is a plastic trait as it responds to growth at elevated temperature, and growth in dry soil
- models should consider night-time conductance and daily minimum conductance as distinctly separate processes.

@@

>>>>

---
title: "On the minimum leaf conductance g~0~"
author: ''
date: ''
output:
  word_document:
    reference_docx: manuscriptstyle.docx
  html_document:
    number_sections: yes
    theme: flatly
csl: global-change-biology.csl
bibliography: references.bib
---

@@

@@

@kala2016 g0 effect heat waves etc.
